---
title: "Linreg specification"
author: "Milda Poceviciute, Henrik Karlsson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linreg specification}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
library(linreg)
data("iris")
```

This vignette summarises the _Least-squares estimation and related techniques_ of linear regression that are available in linreg package.The examples are provided based on Iris data set and linear regression formula:

```{r}
example_formula <- Petal.Length~Sepal.Width+Sepal.Length
```


## General information

The package contains _linreg_ RC object, hence the syntax of calling it is: 

```{r, results = "hide"}
linreg_example <- linreg$new(example_formula, data=iris)
```

The _linreg_ includes calculations of these values:

*    _Estimate of regression coefficients:_
        $$\mathbf{\hat{\mathrm{\beta}}=(X^TX)^{-1}X^Ty}$$
*    _The fitted values:_
        $$\mathbf{\hat{y}=X\hat{\mathrm{\beta}}}$$
*    _The residuals:_
        $$\mathbf{\hat{e}=y-\hat{{y}}}$$
*    _The degrees of freedom:_
        $$df=n-p$$
where $n$ is the number of observations and $p$ is the number of parameters in the model.
*    _The residual variance:_
        $$\hat{\sigma}^2\mathbf{=\frac{e^Te}{df}}$$
*    _The variance of the regression coefficients:_
        $$\mathbf{\widehat{\mathrm{Var}}(\hat{\mathrm{\beta}})}=\hat{\sigma}^2\mathbf{(X^TX)^{-1}}$$
 

## Methods

Below are listed available methods with examples:

*   **print()**, returns the coefficients and coefficient names.
```{r}

linreg_example$print()
```
*   **plot()**, returns _Residuals vs Fitted_ and _Scale−Location_ plots
```{r}

linreg_example$plot()
```

*   **resid()**, returns return the vector of residuals $\mathbf{e}$.(in the example only first 5 values are displayed)
```{r}

residuals <- linreg_example$resid()
residuals[1:5]
```

*   **pred()**, returns the predicted values $\mathbf{\hat{y}}$ (in the example only first 5 values are displayed)
```{r}

predicted <- linreg_example$pred()
predicted[1:5]
```

*   **coef()**, returns the coefficients as a named vector
```{r}

linreg_example$coef()
```

*   **summary()**, returns the coefficients, their standard error, $t-value$, $p-value$, and the degrees of freedom in the model

```{r}

linreg_example$summary()
```


```{r, echo= FALSE}
sessionInfo()
```
